Phenotypes_Planting_2019

### 2020-02-13 data-raw/phenotypes_2019.Rmd
Edit 2019 phenotype data to include BIOMASS REGR LD_EOS

```{r}
phenotypes_2019 <- phenotypes_2019 %>%
  mutate(FRZ_DMG = as.numeric(FRZ_DMG),
         GR1 = as.numeric(GR1),
         GR50 = as.numeric(GR50),
         GR100 = as.numeric(GR100),
         EM1 = as.numeric(EM1),
         EM50 = as.numeric(EM50),
         FL1 = as.numeric(FL1),
         FL50 = as.numeric(FL50),
         TC_EOS = as.numeric(TC_EOS),
         HT_PAN_EOS = as.numeric(HT_PAN_EOS),
         DEAD_2018 = ifelse(is.na(DEAD_2018), 0, DEAD_2018),
         CHLR_101 = as.numeric(CHLR_101),
         CHLR_121 = as.numeric(CHLR_121),
         CHLR_136 = as.numeric(CHLR_136),
         CHLR_JASON_138 = as.numeric(CHLR_JASON_138),
         CHLR_150. = as.numeric(CHLR_150.),
         SPAD_158 = as.numeric(SPAD_158),
         SPADCOR_158 = as.numeric(SPADCOR_158)
         )
```

@@

```{r}
phenotypes_long_2019 <- phenotypes_2019 %>%
  dplyr::select(-SRV, -DEAD_2018) %>%
  dplyr::select(SITE:PLANT_ID, starts_with("NOTE"), everything()) %>%
  pivot_longer(cols = FRZ_DMG:SPADCOR_158, names_to = "PHE", values_to = "Value") %>%
  filter(!is.na(Value)) %>%
  dplyr::select(SITE:PLANT_ID, PHE, Value, everything())

@@

# phenotypes_long_2019$SITE <- factor(phenotypes_long_2019$SITE, levels = c("KING", "PKLE", "TMPL", "OVTN", "STIL", "CLMB", "LINC", "FRMI", "KBSM", "BRKG"))
phenotypes_long_2019$SITE <- factor(phenotypes_long_2019$SITE, levels = c("BRKG", "KBSM", "FRMI", "LINC", "CLMB", "STIL", "OVTN", "TMPL", "PKLE", "KING"))
phenotypes_long_2019$PHE <- factor(phenotypes_long_2019$PHE, levels = c("GR1", "GR50", "GR100", "EM1", "EM50", "FL1", "FL50", "TC_EOS", "HT_PAN_EOS", "FRZ_DMG", "CHLR_101", "CHLR_121", "CHLR_136", "CHLR_JASON_138", "CHLR_150.", "SPAD_158", "SPADCOR_158"))

@@

```{r}
phenotypes_long_2019 %>%
  filter(grepl("TC_EOS", PHE) | grepl("HT_PAN_EOS", PHE) | grepl("FRZ", PHE)) %>%
  ggplot(aes(x = Value)) +
  geom_histogram(aes(fill = SITE)) + 
  facet_grid(SITE~PHE, scales = "free") +
  scale_fill_viridis(discrete = TRUE, end = 0.95, direction = -1) +
  theme(legend.position = "none", axis.text.x = element_text(angle = 45, hjust = 1)) + xlab("Date") + ylab("Number of Individuals")

save_plot("2019_Phenotypic_Data_by_Site_2019-12-30.png", plot = last_plot(), base_height = 10, base_width = 6)
```

>>>>

```{r}
phenotypes_2019 <- phenotypes_2019 %>%
  mutate(FRZ_DMG = as.numeric(FRZ_DMG),
         GR1 = as.numeric(GR1),
         GR50 = as.numeric(GR50),
         GR100 = as.numeric(GR100),
         EM1 = as.numeric(EM1),
         EM50 = as.numeric(EM50),
         FL1 = as.numeric(FL1),
         FL50 = as.numeric(FL50),
         TC_EOS = as.numeric(TC_EOS),
         HT_PAN_EOS = as.numeric(HT_PAN_EOS),
         REGR = as.numeric(REGR),
         LD_EOS = as.numeric(LD_EOS),
         MOISTURE = as.numeric(MOISTURE),
         BIOMASS = as.numeric(BIOMASS),
         DEAD_2018 = ifelse(is.na(DEAD_2018), 0, DEAD_2018),
         CHLR_101 = as.numeric(CHLR_101),
         CHLR_121 = as.numeric(CHLR_121),
         CHLR_136 = as.numeric(CHLR_136),
         CHLR_JASON_138 = as.numeric(CHLR_JASON_138),
         CHLR_150. = as.numeric(CHLR_150.),
         SPAD_158 = as.numeric(SPAD_158),
         SPADCOR_158 = as.numeric(SPADCOR_158)
         )
```

@@

```{r}
phenotypes_long_2019 <- phenotypes_2019 %>%
  dplyr::select(-SRV, -DEAD_2018) %>%
  dplyr::select(SITE:PLANT_ID, starts_with("NOTE"), everything()) %>%
  pivot_longer(cols = FRZ_DMG:T_EM_FL, names_to = "PHE", values_to = "Value") %>%
  filter(!is.na(Value)) %>%
  dplyr::select(SITE:PLANT_ID, PHE, Value, everything())

@@

# phenotypes_long_2019$SITE <- factor(phenotypes_long_2019$SITE, levels = c("KING", "PKLE", "TMPL", "OVTN", "STIL", "CLMB", "LINC", "FRMI", "KBSM", "BRKG"))
phenotypes_long_2019$SITE <- factor(phenotypes_long_2019$SITE, levels = c("BRKG", "KBSM", "FRMI", "LINC", "CLMB", "STIL", "OVTN", "TMPL", "PKLE", "KING"))

unique(phenotypes_long_2019$PHE) # check what phenotypes there are
phenotypes_long_2019$PHE <- factor(phenotypes_long_2019$PHE, levels = c("GR1", "GR50", "GR100", "EM1", "EM50", "FL1", "FL50", "T_GR_EM", "T_GR_FL", "T_EM_FL", "TC_EOS", "HT_PAN_EOS", "REGR", "LD_EOS", "BIOMASS", "MOISTURE", "FRZ_DMG", "CHLR_101", "CHLR_121", "CHLR_136", "CHLR_JASON_138", "CHLR_150.", "SPAD_158", "SPADCOR_158"))

@@

```{r}
phenotypes_long_2019 %>%
  filter(grepl("TC_EOS", PHE) | grepl("HT_PAN_EOS", PHE) | grepl("BIOMASS", PHE) | grepl("MOIST", PHE)) %>%
  ggplot(aes(x = Value)) +
  geom_histogram(aes(fill = SITE)) + 
  facet_grid(SITE~PHE, scales = "free") +
  scale_fill_viridis(discrete = TRUE, end = 0.95, direction = -1) +
  theme(legend.position = "none", axis.text.x = element_text(angle = 45, hjust = 1)) + xlab("Date") + ylab("Number of Individuals")

save_plot("2019_Phenotypic_Data_by_Site_2019-12-30.png", plot = last_plot(), base_height = 10, base_width = 6)

phenotypes_long_2019 %>%
  filter(grepl("MOIST", PHE)) %>% arrange(desc(Value))
phenotypes_long_2019 %>%
  filter(grepl("BIOMASS", PHE)) %>% arrange(desc(Value))
```

SITE  PLOT_GL   PLOT_LC  ACC  PLANT_ID  PHE  Value
KBSM	M5710	5710	J476	J476.C	MOISTURE	-1154.137931	NA	NA	
KBSM	M4412	4412	J024	J024.A	MOISTURE	-195.065147
KBSM	M6607	6607	J646	J646.A	MOISTURE	973.34815

KBSM	M5710	5710	J476	J476.C	BIOMASS	19439.138
